The increasing cost of happiness

### 2020-09-05 src/The increasing cost of happiness.Rmd
Updated draft

---
title: "The increasing cost of happiness"
author: "Dr Richard Morris"
date: "Updated: `r Sys.Date()`"
bibliography: references.bib
csl: elsevier-harvard.csl
output: github_document
---

@@

## Abstract
Goes here.

@@

For instance, one [survey of 1,000 Americans](https://www.pnas.org/content/107/38/16489.full){target="_blank"}, conducted in 2010, concluded that money does make us happier – but only up to a certain point. The findings showed that self-reported levels of happiness increased with household wealth up to \$75,000 a year. But after that, increasing amounts of money had no further effect on happiness [@kahneman2010high]. Results such as these have reinforced the view among psychologists and economists that the relationship between income and measures of subjective wellbeing, such as happiness, increases linearly up to a point after which there is little gained by further increments in income [@clark2018four; @dolan2008we].

>>>>

---
title: "The increasing cost of happiness"
author: "Dr Richard Morris"
date: "Updated: `r Sys.Date()`"
bibliography: references.bib
csl: elsevier-harvard.csl
output: 
  html_document:
    keep_md: true
---

@@

## Abstract
A fundamental question for governments and people is how much happiness does a dollar buy? The accepted view among economists and psychologists is that money and happiness increase together up to a point, after which there is little further gain from increasing wealth. While the location of this _change point_ has been determined, and the cost of happiness reportedly ranges between USD\$60-95K, there has been no investigation as to whether the cost of happiness has increased or decreased over time.

@@

For instance, one [survey of 1,000 Americans](https://www.pnas.org/content/107/38/16489.full){target="_blank"}, conducted in 2010, concluded that money does make us happier – but only up to a certain point. The findings showed that self-reported levels of happiness increased with household wealth up to \$75,000 a year. But after that, increasing amounts of money had no further effect on happiness [@kahneman2010high]. Results such as these have reinforced the view among psychologists and economists that the relationship between wealth and measures of subjective wellbeing, such as happiness, increases linearly up to a point after which there is little gained by further increments in wealth [@clark2018four; @dolan2008we].
